### 2011-01-22 paper/learningMethods.tex

The nine subscripted functions correspond to the nine labeled motors in \figref{robotDiagram}

@@

>>>>

\edit{make figure to go here, show drawing with inner/outer, l/r, and f/b motors.}
\edit{JMC: Use photo of physical robot in this image, and add labels in photoshop?}
The nine subscripted functions correspond to the nine labeled motors in \figref{robotDiagram}

@@

\edit{JMC:Bullets=narrower column=wasted space. subsubsection instead?}
